\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}

\title{Introduction to Microsoft Azure{}}
\author{Neelam Shah}

\maketitle



\section{Microsoft Azure}
Here is the text of your introduction.



\subsection{Create free Azure account}
\begin{itemize}
	\item You can create one year free azure account by signing up to the following link: \\
	\url{https://azure.microsoft.com/en-us/free/}\\
	This will take credit card details. But don't worry! Your subscription will only become valid after confirmation.
\end{itemize}

\subsection{Learn by Practice}
\begin{itemize}
	\item You can practice using hands-on lab. Microsoft has created hands-on labs which can be accessed following the link below: \\
	\url{https://www.microsoft.com/handsonlabs}\\
	
	\item Sometimes we might have access to corporate Azure account, but we don't know how to practice. So, there is a site whose link is given below:\\
	\url{https://azurecitadel.github.io/labs}\\
	A number of things is available to give idea about what can be done with Azure.
	
	\item You can also learn using the link given below:\\
	\url{https://microsoftlearning.github.io/20533-ImplementingMicrosoftAzureInfrastructureSolutions/}\\
	
	\item You can also learn using the link given below:\\
	\url{https://docs.microsoft.com/en-us/learn/}
\end{itemize}


\subsection{Amazing Azure Resources}
Here are some official Microsoft websites that you really should bookmark when studying for the 70-535 exam:
\begin{itemize}
	\item Azure Code Samples:\\
	\url{https://azure.microsoft.com/en-us/resources/samples/?sort=0}
	
	\item Official Azure Documentation:\\
	\url{https://docs.microsoft.com/en-us/azure/}
	
	\item Azure Citadel - Labs and Workshops:\\
	\url{https://azurecitadel.github.io/labs/}
	
	\item Azure Hands on Labs:\\
	\url{https://handsonlabs-r.azurewebsites.net/}
	
	\item Official Microsoft Azure YouTube Channel:\\
	\url{https://www.youtube.com/user/windowsazure}
	
	\item Official Microsoft Developer YouTube Channel:\\
	\url{https://www.youtube.com/channel/UCsMica-v34Irf9KVTh6xx-g}
	
	\item Download the Azure SDK's for .NET, PowerShell, CLI and other languages:\\
	\url{https://azure.microsoft.com/en-us/downloads/}
	
	\item Official Github Repository for PowerShell Scripts:\\
	\url{https://github.com/Azure/azure-powershell}
	
	\item Azure REST API Browser:\\
	\url{https://docs.microsoft.com/en-us/rest/api/?view=Azure}
	
\end{itemize}



\section{Conclusion}
Write your conclusion here.

\end{document}